Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and other entertaining math in Coq

### 2021-09-09 doc/JFLA2022/paper.tex
draft paper

@@

@@

Since the set \texttt{AP} of additive principals  is closed under addition
(by Lemma \texttt{AP\_plus\_closed}, it suffices to prove the inequalities $\omega<\phi_0(2)$ and $42<\phi_0(2)$.

@@

\section{Perspectives}
The Gaia project~\cite{Gaia}, also maintained on \texttt{Coq-community} contains a development by José Grimm~\cite{grimm:hal-00911710}. This library -- dedicated  to the implementaion in \textit{Coq (SSreflect)} of books from  Bourbaki's Elements of Mathematics --- contains a generalization of two types of ordinals (\texttt{T1} for the ordinal $\epsilon_0$ and
\texttt{T2} for $\Gamma_0$) to a larger ordinal defined by Ackermann, and relates these data structures with Bourbaki's set theory.
It is interesting to note that both libraries \texttt{Gaia} and \texttt{hydra-battles} contain their own (isomorphic) definitions of
\texttt{T1} and \texttt{T2}, originated in~\cite{CantorContrib}.
The types --- defined in different modules --- cannot be considered as equal. Even more, some operations like addition, multiplication, etc. have now different definitions.

It would be interesting to build a library which could be used as a gate giving access to both the combinatorial results of \texttt{hydra-battles} and the set-theoretic content of \texttt{Gaia}.
For instance, the associativity of multiplication of ordinals below $\epsilon_0$, already proven in \texttt{Gaia} could be tranferred ``for free'' to the data structures of \texttt{hydra-battles}, thanks to the isomorphism between both implementations.

\section{Acknowledgments}
\label{sect:acks}

>>>>

\newtheorem{todo}{To do}

@@

\begin{todo}
  Relation with Russel's library (maintained in Coq-community).
\end{todo}

@@

Since the set \textit{AP} of additive principals  is closed under addition
(by Lemma \textit{AP\_plus\_closed}, it suffices to prove the inequalities $\omega<\phi_0(2)$ and $42<\phi_0(2)$.

@@

\section{Perspectives}
The Gaia project~\cite{Gaia}, also maintained on \textit{Coq-community} contains a development by José Grimm~\cite{grimm:hal-00911710}. This library -- dedicated  to the implementaion in \textit{Coq (SSreflect)} of books from  Bourbaki's Elements of Mathematics --- contains a generalization of two types of ordinals (\texttt{T1} for the ordinal $\epsilon_0$ and
\texttt{T2} for $\Gamma_0$) to a larger ordinal defined by Ackermann, and relates these data structures with Bourbaki's set theory.
It is interesting to note that both libraries \textit{Gaia} and \textit{hydra-battles} contain their own (isomorphic) definitions of
\texttt{T1} and \texttt{T2}, originated in~\cite{CantorContrib}.
The types --- defined in different modules --- cannot be considered as equal. Even more, some operations like addition, multiplication, etc. have now different definitions.

It would be interesting to build a library which could be used as a gate giving access to both the combinatorial results of \textit{hydra-battles} and the set-theoretic content of \textit{Gaia}.
For instance, the associativity of multiplication of ordinals below $\epsilon_0$, already proven in \textit{Gaia} could be tranferred ``for free'' to the data structures of \textit{hydra-battles}, thanks to the isomorphism between both implementations.

%\section{Acknowledgments}
%\label{sect:acks}
